### 2019-10-10 tim-lucas-model-ensembles.tex
Switch table columns.

We used two data sources that reflect \emph{Plasmodium falciparum} malaria transmission; point-prevalence surveys and polygon-level, aggregated incidence data. 
We selected Madagascar, Colombia, Indonesia and Senegal as case examples as they all have fairly complete, publicly available, surveillance data at a finer geographical resolution than admin 1.
The prevalence survey data were extracted from the Malaria Atlas Project prevalence survey database using only data from 1990 onwards \citep{bhatt2015effect, guerra2007assembling, pfeffer2018ma}.
The prevalence points were then standardised to an age range of 2--10 using the model from \citep{smith2007standardizing}.

@@

\begin{table}[h!]
\caption{Pearson correlations between observed and predicted values. }
\centering
\begin{tabular}{llrrrr}
Cross-validation scheme & Country &  Enviro &  ML\textsubscript{l} &  Enviro + ML\textsubscript{l} \\
\hline 
 Random &  Colombia & 0.59 & 0.59 & \textbf{0.61} \\
 Spatial &  Colombia &  0.12 &  \textbf{0.33} &  0.25\\
 Random &  Madagascar &  0.70 &  \textbf{0.73} & 0.69 \\
 Spatial &  Madagascar &  0.22 &  \textbf{0.66} & 0.18\\
 Random &  Senegal &  \textbf{0.58} &  0.51 & 0.57 \\
 Spatial &  Senegal &  \textbf{0.63} &  0.27 &  \textbf{0.63} \\
 Random &  Indonesia &  0.52 &  0.48 &  \textbf{0.59} \\
 Spatial &  Indonesia &  0.45 &  0.44 &  \textbf{0.51} \\
\end{tabular}
\label{t:results}
\end{table}

\begin{table}[h!]
\caption{Pearson correlations between observed and predicted values. }
\centering
\begin{tabular}{llrrrr}
Cross-validation scheme & Country &  Covariates &   ML\textsubscript{g} & ML\textsubscript{l} + ML\textsubscript{g} \\
\hline 
 Random &  Colombia & \textbf{0.59} &0.58 & 0.56 \\
 Spatial &  Colombia &  0.12 &  0.18 & \textbf{0.34}\\
 Random &  Madagascar &  0.70 &  0.70 & \textbf{0.71} \\
 Spatial &  Madagascar &  0.22 &  \textbf{0.63} & 0.60\\
 Random &  Senegal &  \textbf{0.58} &  0.30 & 0.08 \\
 Spatial &  Senegal &  \textbf{0.63} & 0.36 & 0.35 \\
 Random &  Indonesia &  \textbf{0.52} & 0.46 & 0.32 \\
 Spatial &  Indonesia &  \textbf{0.45} & 0.41 & \textbf{0.45} \\
\end{tabular}
\label{t:results2}
\end{table}

@@

>>>>

We used two data sources that reflect \emph{Plasmodium falciparum} malaria transmission; point-prevalence surveys and polygon-level, aggregated incidence data. 
We selected Madagascar, Colombia, Indonesia and Senegal as case examples as they all have fairly complete, publicly available, surveillance data at a finer geographical resolution than admin 1.
The prevalence survey data were extracted from the Malaria Atlas Project prevalence survey database using only data from 1990 onwards \citep{bhatt2015effect, guerra2007assembling, pfeffer2018ma}.
While the data cover a large time period, we did not model time explicitely but future work could include this component.
The prevalence points were then standardised to an age range of 2--10 using the model from \citep{smith2007standardizing}.

@@

\begin{table}[h!]
\caption{Pearson correlations between observed and predicted values. }
\centering
\begin{tabular}{llrrrr}
Country &  Cross-validation & Enviro &  ML\textsubscript{l} &  Enviro + ML\textsubscript{l} \\
\hline 
 Colombia & Random &  0.59 & 0.59 & \textbf{0.61} \\
 Colombia &  Spatial &  0.12 &  \textbf{0.33} &  0.25\\
 Madagascar & Random &   0.70 &  \textbf{0.73} & 0.69 \\
 Madagascar &  Spatial &  0.22 &  \textbf{0.66} & 0.18\\
 Senegal &  Random &  \textbf{0.58} &  0.51 & 0.57 \\
 Senegal &  Spatial &  \textbf{0.63} &  0.27 &  \textbf{0.63} \\
 Indonesia &  Random &  0.52 &  0.48 &  \textbf{0.59} \\
 Indonesia &  Spatial &  0.45 &  0.44 &  \textbf{0.51} \\
\end{tabular}
\label{t:results}
\end{table}

\begin{table}[h!]
\caption{Pearson correlations between observed and predicted values. }
\centering
\begin{tabular}{llrrrr}
Country &  Cross-validation & Enviro &   ML\textsubscript{g} & ML\textsubscript{l} + ML\textsubscript{g} \\
\hline 
 Colombia & Random &  \textbf{0.59} &0.58 & 0.56 \\
 Colombia &  Spatial &  0.12 &  0.18 & \textbf{0.34}\\
 Madagascar &  Random &  0.70 &  0.70 & \textbf{0.71} \\
 Madagascar &  Spatial &  0.22 &  \textbf{0.63} & 0.60\\
 Senegal &  Random &  \textbf{0.58} &  0.30 & 0.08 \\
 Senegal &  Spatial &  \textbf{0.63} & 0.36 & 0.35 \\
 Indonesia &  Random &  \textbf{0.52} & 0.46 & 0.32 \\
 Indonesia &  Spatial &  \textbf{0.45} & 0.41 & \textbf{0.45} \\
\end{tabular}
\label{t:results2}
\end{table}

@@

\begin{table}[h!]
\caption{Covarage of 80\% credible intervals. }
\centering
\begin{tabular}{llrrrr}
CV & Country &  Enviro & ML\textsubscript{g} & ML\textsubscript{l} + ML\textsubscript{g} \\
\hline 
 Random &  Colombia &  \\
 Spatial &  Colombia &  \\
 Random &  Madagascar &  \\
 Spatial &  Madagascar & \\
 Random &  Senegal & \\
 Spatial &  Senegal &  \\
 Random &  Indonesia &  \\
 Spatial &  Indonesia &   \\
\end{tabular}
\label{t:results2}
\end{table}
